01_LH-SIP_Data_Reduction

### 2022-05-24 01_LH-SIP_Data_Reduction.Rmd
removed deprecated export fn

FID_results_PAIBE_ug <- FID_results %>% 
  select(
    sample_id, 
    file,
    compound,
    area_FID, 
    rel_area_FID) %>% 
  filter(compound == "PAIBE") %>% 
  mutate(
    PAIBE_area = area_FID,
    PAIBE_ug_inj = 0.1, # PAIBE injected = (10µg/100µL*1µL) = 0.1µg
    # Find instrument response as PAIBE mass per FID area
    ug_per_area = PAIBE_ug_inj / PAIBE_area,
    # Check that the inferred mass is the same as known mass
    PAIBE_ug_inj_inferred = ug_per_area * PAIBE_area
  ) %>%
  select(file, PAIBE_area, PAIBE_ug_inj, ug_per_area)

@@

# For 0 -3, 0-7 timepoints
peaks_mapped_with_zeros_FID_mc_pame <- peaks_mapped_with_zeros_FID %>% 
  left_join(compound_nC_nH, by = "compound") %>% 
  mutate(`2F_Me` = PAME_summarized %>% pull(at2H_mn),
         # define calibrated 2F
         `2F_FAME` = calibrated_at2H_without_memory,
         `2F_alk` = (`2F_FAME` - `2F_Me`*x_me) / x_alk,
         # define calibrated 2F mc
         `2F_FAME_mc` = calibrated_at2H_with_memory_correction,
         `2F_alk_mc` = (`2F_FAME_mc` - `2F_Me`*x_me) / x_alk)
```

@@

saveRDS(peaks_mapped_with_threes_analytes_reduced,
        file = "cache/LH_SIP_data_3d_onwards.RDS")

>>>>

FID_results_PAIBE_ug <- FID_results %>% 
  select(
    sample_id, 
    file,
    compound,
    area_FID, 
    rel_area_FID
  ) %>% 
  filter(compound == "PAIBE") %>% 
  mutate(
    PAIBE_area = area_FID,
    PAIBE_ug_inj = 0.1, # PAIBE injected = (10µg/100µL*1µL) = 0.1µg
    # Find instrument response as PAIBE mass per FID area
    ug_per_area = PAIBE_ug_inj / PAIBE_area,
    # Check that the inferred mass is the same as known mass
    PAIBE_ug_inj_inferred = ug_per_area * PAIBE_area
  ) %>%
  select(file, PAIBE_area, PAIBE_ug_inj, ug_per_area)

@@

peaks_mapped_with_zeros_FID_mc_pame <- peaks_mapped_with_zeros_FID %>% 
  left_join(compound_nC_nH, by = "compound") %>% 
  mutate(`2F_Me` = PAME_summarized %>% pull(at2H_mn),
         # define calibrated 2F
         `2F_FAME` = calibrated_at2H_without_memory,
         `2F_alk` = (`2F_FAME` - `2F_Me`*x_me) / x_alk,
         # define calibrated 2F mc
         `2F_FAME_mc` = calibrated_at2H_with_memory_correction,
         `2F_alk_mc` = (`2F_FAME_mc` - `2F_Me`*x_me) / x_alk)
```

@@
